SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-17 SDM_the_search_for_powers_of_2_everywhere.tex
details, jupyter --> talex, etc

\documentclass[11pt]{article}
	\usepackage{nopageno}

@@

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Kanerva-Table-7.3}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{k+kn}{import} \PY{n+nn}{sdm} \PY{k+kn}{as} \PY{n+nn}{sdmlib}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{o}{\PYZpc{}}\PY{k}{matplotlib} inline
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}3}]:} \PY{k}{def} \PY{n+nf}{gen\PYZus{}sdm}\PY{p}{(}\PY{n}{scanner\PYZus{}type}\PY{p}{,} \PY{n}{bits}\PY{o}{=}\PY{l+m+mi}{1000}\PY{p}{,} \PY{n}{sample}\PY{o}{=}\PY{l+m+mi}{1000000}\PY{p}{)}\PY{p}{:}
            \PY{n}{address\PYZus{}space} \PY{o}{=} \PY{n}{sdmlib}\PY{o}{.}\PY{n}{AddressSpace}\PY{o}{.}\PY{n}{init\PYZus{}from\PYZus{}b64\PYZus{}file}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sdm\PYZhy{}10000w.as}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
            \PY{n}{counter} \PY{o}{=} \PY{n}{sdmlib}\PY{o}{.}\PY{n}{Counter}\PY{o}{.}\PY{n}{load\PYZus{}file}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sdm\PYZhy{}10000w}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
            \PY{n}{sdm} \PY{o}{=} \PY{n}{sdmlib}\PY{o}{.}\PY{n}{SDM}\PY{p}{(}\PY{n}{address\PYZus{}space}\PY{p}{,} \PY{n}{counter}\PY{p}{,} \PY{l+m+mi}{451}\PY{p}{,} \PY{n}{scanner\PYZus{}type}\PY{p}{)}
            \PY{k}{return} \PY{n}{sdm}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}4}]:} \PY{n}{sdm} \PY{o}{=} \PY{n}{gen\PYZus{}sdm}\PY{p}{(}\PY{n}{sdmlib}\PY{o}{.}\PY{n}{SDM\PYZus{}SCANNER\PYZus{}OPENCL}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{n}{b} \PY{o}{=} \PY{n}{sdmlib}\PY{o}{.}\PY{n}{Bitstring}\PY{o}{.}\PY{n}{init\PYZus{}random}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{)}
        \PY{n}{sdm}\PY{o}{.}\PY{n}{write}\PY{p}{(}\PY{n}{b}\PY{p}{,} \PY{n}{b}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}6}]:} \PY{k+kn}{from} \PY{n+nn}{IPython.display} \PY{k+kn}{import} \PY{n}{clear\PYZus{}output}

        \PY{n}{distances} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{1001}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{)}
        \PY{k}{for} \PY{n}{i}\PY{p}{,} \PY{n}{dist} \PY{o+ow}{in} \PY{n+nb}{enumerate}\PY{p}{(}\PY{n}{x}\PY{p}{)}\PY{p}{:}
            \PY{n}{clear\PYZus{}output}\PY{p}{(}\PY{n}{wait}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
            \PY{k}{print} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Distance: \PYZob{}:4d\PYZcb{} (\PYZob{}:.2f\PYZcb{}}\PY{l+s+s1}{\PYZpc{}}\PY{l+s+s1}{)}\PY{l+s+s1}{\PYZsq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{dist}\PY{p}{,} \PY{l+m+mf}{100.}\PY{o}{*}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{/}\PY{n+nb}{len}\PY{p}{(}\PY{n}{x}\PY{p}{)}\PY{p}{)}
            \PY{n}{c} \PY{o}{=} \PY{n}{sdmlib}\PY{o}{.}\PY{n}{Bitstring}\PY{o}{.}\PY{n}{init\PYZus{}from\PYZus{}bitstring}\PY{p}{(}\PY{n}{b}\PY{p}{)}
            \PY{n}{c}\PY{o}{.}\PY{n}{flip\PYZus{}random\PYZus{}bits}\PY{p}{(}\PY{n}{dist}\PY{p}{)}
            \PY{k}{assert} \PY{n}{c}\PY{o}{.}\PY{n}{distance\PYZus{}to}\PY{p}{(}\PY{n}{b}\PY{p}{)} \PY{o}{==} \PY{n}{dist}
            \PY{n}{d} \PY{o}{=} \PY{n}{sdm}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{n}{c}\PY{p}{)}
            \PY{n}{distances}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{d}\PY{o}{.}\PY{n}{distance\PYZus{}to}\PY{p}{(}\PY{n}{b}\PY{p}{)}\PY{p}{)}
        \PY{k}{print} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Done!}\PY{l+s+s1}{\PYZsq{}}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Distance: 1000 (100.00\%)
Done!

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}29}]:} \PY{n}{plt}\PY{o}{.}\PY{n}{figure}\PY{p}{(}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{distances}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{x}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{p}{[}\PY{l+m+mi}{500}\PY{p}{]}\PY{o}{*}\PY{n+nb}{len}\PY{p}{(}\PY{n}{x}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Kanerva}\PY{l+s+se}{\PYZbs{}\PYZsq{}}\PY{l+s+s1}{s Figure 7.3}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{New distance (after one read)}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Old distance}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{axis}\PY{p}{(}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{]}\PY{p}{)}\PY{p}{;}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_5_0.png}
    \end{center}
    { \hspace*{\fill} \\}

>>>>

\documentclass[11pt]{article}

@@

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{SDM\_the\_search\_for\_powers\_of\_2\_everywhere}

@@

    \maketitle

    \section{Sparse Distributed Memory: How many
subspaces?}\label{sparse-distributed-memory-how-many-subspaces}

In his original analysis, Kanerva uses... ...1,000 dimensions
...1,000,000 circles ...with radius=451 bits so that a random bistring
will be stored in aproximately 1,000 hard locations.

A first observation here is that powers of 10 are not well suited,
either for the mathematical analysis of the space, or for computer
science. Let us play a little with numbers here, starting from Kanerva's
parameters. Our goal will be to find how many circles we should use and
the radius of a circle. Can we find some optimum set of parameters?

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}3}]:} \PY{n}{n} \PY{o}{=} \PY{l+m+mi}{1000} \PY{c+c1}{\PYZsh{} number of dimensions}
        \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{number of dimensions=}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}\PY{n}{n}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
number of dimensions= 1000

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}4}]:} \PY{k}{def} \PY{n+nf}{mu}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{:}
            \PY{k}{return} \PY{n}{n}\PY{o}{/}\PY{l+m+mi}{2}

        \PY{k+kn}{import} \PY{n+nn}{math}

        \PY{k}{def} \PY{n+nf}{sigma}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{:}
            \PY{k}{return} \PY{n}{math}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}

        \PY{k}{def} \PY{n+nf}{percentage\PYZus{}of\PYZus{}n}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{:}
            \PY{k}{return} \PY{p}{(}\PY{l+m+mi}{100}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{6}\PY{o}{*}\PY{n}{sigma}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{)}\PY{p}{)} \PY{o}{/} \PY{n}{n}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k}{def} \PY{n+nf}{analysis}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{:}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{************ ANALYSIS FOR n=}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}\PY{n}{n}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{orthoghonal distance=}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}\PY{n}{mu}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{standard deviation=}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}\PY{n}{sigma}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{the space offers }\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n+nb}{str}\PY{p}{(}\PY{n}{n}\PY{o}{/}\PY{o}{/}\PY{n}{sigma}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ standard deviations.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{3 sigma=}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+m+mf}{3.09}\PY{o}{*}\PY{n}{sigma}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{the distance from a pole to the equator=}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{math}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{standard deviations}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{the percentage of n (in relation to the range R Bits) is}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{percentage\PYZus{}of\PYZus{}n}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{)}\PY{c+c1}{\PYZsh{} When using mu \PYZhy{} 3 sigma...}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Because 3 standard deviations contain \PYZti{}1/1000 of a normal distribution, }\PY{l+s+s1}{\PYZsq{}} \PYZbs{}
                    \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{approximately one in a thousand items will be found in a circle of}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PYZbs{}
                    \PY{n}{mu}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{l+m+mf}{3.09}\PY{o}{*}\PY{n}{sigma}\PY{p}{(}\PY{n}{n}\PY{p}{)}\PY{p}{,}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ radius}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
            \PY{n+nb}{print} \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{...........................................}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}6}]:} \PY{k}{for} \PY{n}{n} \PY{o+ow}{in} \PY{p}{[}\PY{l+m+mi}{100}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{10000}\PY{p}{,} \PY{l+m+mi}{256}\PY{p}{,} \PY{l+m+mi}{1024}\PY{p}{]}\PY{p}{:}
            \PY{n}{analysis}\PY{p}{(}\PY{n}{n}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
************ ANALYSIS FOR n= 100
orthoghonal distance= 50.0
standard deviation= 5.0
the space offers  20.0  standard deviations.
3 sigma= 15.45
the distance from a pole to the equator= 10.0 standard deviations
the percentage of n (in relation to the range R Bits) is 30.0
Because 3 standard deviations contain \textasciitilde{}1/1000 of a normal distribution, approximately one in a thousand items will be found in a circle of 34.55  radius
{\ldots}

************ ANALYSIS FOR n= 1000
orthoghonal distance= 500.0
standard deviation= 15.811388300841896
the space offers  63.0  standard deviations.
3 sigma= 48.857189849601454
the distance from a pole to the equator= 31.622776601683793 standard deviations
the percentage of n (in relation to the range R Bits) is 9.486832980505138
Because 3 standard deviations contain \textasciitilde{}1/1000 of a normal distribution, approximately one in a thousand items will be found in a circle of 451.14281015039853  radius
{\ldots}

************ ANALYSIS FOR n= 10000
orthoghonal distance= 5000.0
standard deviation= 50.0
the space offers  200.0  standard deviations.
3 sigma= 154.5
the distance from a pole to the equator= 100.0 standard deviations
the percentage of n (in relation to the range R Bits) is 3.0
Because 3 standard deviations contain \textasciitilde{}1/1000 of a normal distribution, approximately one in a thousand items will be found in a circle of 4845.5  radius
{\ldots}

************ ANALYSIS FOR n= 256
orthoghonal distance= 128.0
standard deviation= 8.0
the space offers  32.0  standard deviations.
3 sigma= 24.72
the distance from a pole to the equator= 16.0 standard deviations
the percentage of n (in relation to the range R Bits) is 18.75
Because 3 standard deviations contain \textasciitilde{}1/1000 of a normal distribution, approximately one in a thousand items will be found in a circle of 103.28  radius
{\ldots}

************ ANALYSIS FOR n= 1024
orthoghonal distance= 512.0
standard deviation= 16.0
the space offers  64.0  standard deviations.
3 sigma= 49.44
the distance from a pole to the equator= 32.0 standard deviations
the percentage of n (in relation to the range R Bits) is 9.375
Because 3 standard deviations contain \textasciitilde{}1/1000 of a normal distribution, approximately one in a thousand items will be found in a circle of 462.56  radius
{\ldots}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}86}]:} \PY{n}{print\PYZus{}analysis}\PY{p}{(}\PY{l+m+mi}{1024}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
************ ANALYSIS FOR n= 1024
orthoghonal distance= 512.0
standard deviation= 16.0
3 sigma= 48.0
the distance from a pole to the equator= 32.0 standard deviations
the percentage of n (in relation to the range R Bits) is 9.375
Because 3 standard deviations contain \textasciitilde{}1/1000 of a normal distribution, approximately one in a thousand items will be found in a circle of 464.0  radius
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#

    Let us focus on the word \emph{aproximately}. The estimation is given by
usual tables with metrics of the normal curve.

The \emph{unit} of analysis provided is that of the standard deviation.

Our intention is to make the bit the unit of analysis, and estimate the
statistics of the system in a more precise form.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:}
\end{Verbatim}
